\acknowledgements{
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics
I would like to express my deepest gratitude to my primary advisor, Prof. Dr. Walt Detmar Meurers, for their invaluable guidance and support throughout my master's studies. Their thoughtful feedback, generous mentorship and dedication to overseeing this thesis have been instrumental in shaping my research. I also deeply appreciated the opportunity to work in the Language and Ai in Education lab at the IWM and learn from their lectures.

I am also sincerely grateful to my second advisor, Prof. Dr. Xiaobin, for their support during my time at the Hector Institute while working on the Aisla project, and the insightful perspectives shared in their lectures which greatly enriched my academic experience.

A special thanks goes to Prof. Dr. Mutsuko Endo Hudson, whose enthisiastic encouragement meant a great deal to me. Their insightful suggestions, particularly regarding JLPT grammar forms, played a significant role in the development of this thesis.

I would also like to thank my husband for his unwavering support and encouragement throughout my master's studies. His willingness to cook, taking the children out so I could concentrate, and to cheer me on during the difficult moments made this thesis possible in more ways than one.

Finally, to my children-thank you for helping out around the house, for celebrating each milestone with me, and for bringing joy to this long and challenging process. Each page written was made lighter by your smiles.

}
\clearpage